### 2020-09-28 priority-gv.tex

@@

\begin{definition}[Actions]
  \label{def:pgv-actions}
  A~term acts on an endpoint $\tm{x}$ if it is in one of the following forms:
  \begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item $\tm{\link\;\pair{x}{y}}$ 
    \item $\tm{\link\;\pair{y}{x}}$
    \item $\tm{\send\;\pair{x}{y}}$
    \item $\tm{\recv\;{x}}$
    \item $\tm{\close\;{x}}$
    \item $\tm{\wait\;{x}}$
    \end{itemize}
  \end{multicols}
  \noindent
  A~term is an action if it acts on some endpoint $\tm{x}$.
\end{definition}

\begin{definition}[Ready Actions]
  \label{def:pgv-ready-actions}
  A~term is ready to act on an endpoint $\tm{x}$ if it is of the form $\tm{\plug{E}{M}}$, where $\tm{M}$ acts on $\tm{x}$. A~term is ready if it is ready to act on some endpoint $\tm{x}$.
\end{definition}

\begin{restatablelemma}{lempgvprogressterms}[Open Progress, $\tred$]

\end{restatablelemma}

\begin{definition}[Canonical Forms]
  \label{def:pgv-canonical-forms}
  A~configuration $\tm{\conf{C}}$ is in canonical form if it is of the following form:
  \[
    \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;N)}}}
  \]
\end{definition}

@@

\begin{restatabletheorem}{thmpgvclosedprogressconfs}[Closed Progress, $\cred$]
  \label{lem:pgv-closed-progress-confs}
  If $\cseq[\main]{\emptyenv}{\conf{C}}$ and $\tm{\conf{C}}$ is in canonical form, then either $\tm{\conf{C}}=\tm{\main\;V}$ or there exists a $\tm{\conf{D}}$ such that $\tm{\conf{C}}\cred\tm{\conf{D}}$.
\end{restatabletheorem}
\begin{proof}
  \label{prf:thm-pgv-closed-progress}
  Let $\tm{\conf{C}}=\tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;N)}}}$. If any term $\tm{M_i}$ or $\tm{N}$ is \emph{not} ready, 
\end{proof}

  % Pick the process $\tm{P_i}$ with the smallest priority $\minpr{(\ty{\Gamma_i})}$. $\tm{P_i}$ acts on some endpoint $\tmty{y}{A}\in\ty{\Gamma_i}$. We must have $\minpr{(\ty{\Gamma_i})}=\pr{(\ty{A})}$, since the other actions in $\tm{P_i}$ are guarded by the action on $\tmty{y}{A}$.

  % If $\tm{P_j}$ is a link $\tm{\link{y}{z}}$ or $\tm{\link{z}{y}}$, we apply \LabTirName{E-Link}.

  % Otherwise, there must be a process $\seq{P_j}{\ty{\Gamma_j}}$ where $\tmty{y'}{\co{A}}\in\ty{\Gamma_j}$ and $\tm{y}$ and $\tm{y'}$ are dual endpoints of the same channel, since $\tm{y}$ is bound. By duality, $\pr{(\ty{A})}=\pr{(\ty{\co{A}})}$. We must have $\pr{(\ty{\co{A}})}=\minpr{(\ty{\Gamma_j})}$, since we chose $\tm{P_i}$ to have the smallest priority $\minpr{(\Gamma_i)}$. We cannot have $\tm{P_i}=\tm{P_j}$, otherwise the action on $\tm{y'}$ would be guarded by the action on $\tm{y}$, requiring $\pr{(\ty{A})}<\pr{(\ty{\co{A}})}$. The process $\tm{P_j}$ must act on $\tm{y'}$, otherwise the action on $\tm{y'}$ would be guarded by another action with priority smaller than $\pr{(\ty{A})}$. We have two processes, acting on dual endpoints. We apply the appropriate reduction rule, \ie \LabTirName{E-Send}, \LabTirName{E-Close}, \LabTirName{E-Select-Inl}, or \LabTirName{E-Select-Inr}.

>>>>

\todo{Define the ``priority bound of a term $\tm{M}$'' as $\cs{p}$ where $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$.}

@@

\begin{definition}[Actions]
  \label{def:pgv-actions}
  A~term acts on an endpoint $\tm{x}$ if it is in one of the following forms:
  \begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item $\tm{\link\;\pair{x}{y}}$ 
    \item $\tm{\link\;\pair{y}{x}}$
    \item $\tm{\send\;\pair{V}{x}}$
    \item $\tm{\recv\;{x}}$
    \item $\tm{\close\;{x}}$
    \item $\tm{\wait\;{x}}$
    \end{itemize}
  \end{multicols}
  \noindent
  A~term is an action if it acts on some endpoint $\tm{x}$.
\end{definition}

\begin{definition}[Ready Terms]
  \label{def:pgv-ready-actions}
  A~term $\tm{L}$ is ready if it is of the form $\tm{\plug{E}{M}}$, where $\tm{M}=\tm{\new}$, $\tm{M}=\tm{\spawn\;N}$, or $\tm{M}$ acts on $\tm{x}$. In the latter case, we say that $\tm{L}$ is ready to act on $\tm{x}$.
\end{definition}

\begin{restatablelemma}{lempgvreadypriority}
  \label{lem:pgv-ready-priority}
  If $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$ is ready, then $\cs{p}=\cs{o}$ for some priority $\cs{o}$.
\end{restatablelemma}
\begin{proof}
  \admit
\end{proof}

\begin{restatablelemma}{lempgvopenprogressterms}[Open Progress, $\tred$]
  \label{lem:pgv-open-progress-terms}
  If $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$, then:
  \begin{itemize}
  \item $\tm{M}$ is a value;
  \item $\tm{M}\tred\tm{N}$ for some term $\tm{N}$; or
  \item $\tm{M}$ is ready.
  \end{itemize}
\end{restatablelemma}
\begin{proof}
  \admit
\end{proof}

\begin{definition}[Canonical Forms]
  \label{def:pgv-canonical-forms}
  A~configuration $\tm{\conf{C}}$ is in canonical form if it is of the following form, where no term $\tm{M_i}$ is a value:
  \[
    \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;N)}}}
  \]
\end{definition}

@@

\begin{restatabletheorem}{thmpgvclosedprogressconfs}[Closed Progress, $\cred$]
  \label{lem:pgv-closed-progress-confs}
  If $\cseq[\main]{\emptyenv}{\conf{C}}$ and $\tm{\conf{C}}$ is in canonical form, then either $\tm{\conf{C}}\cred\tm{\conf{D}}$ for some $\tm{\conf{D}}$; or
  \[
    \tm{\conf{C}}
    =
    \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;V)}}},
  \]
  where each $\tm{M_i}$ is ready to act on $\tm{x_i}$.
\end{restatabletheorem}
\begin{proof}
  Details in \cref{prf:thm-pgv-closed-progress-confs}.
\end{proof}
